Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-23 writeups/dissertation/dissertation.tex
foo

\tectcite{Anderson1991} also used tasks similar to tag use on StackOverflow and Twitter when deriving the prior component of the declarative memory theory.
\citeauthor{Anderson1991} examined, for example, the frequency of word choice over time used for the title of articles for the New York Times,
and used the results to derive the power law equation for the prior term in the declarative memory model.
ACT-R's declarative memory theory claims that the system has evolved to make predictions that closely match the statistical structure of the environment.
Using a power-law equation to model future tag use based on past tag use is a reasonable statistical approach to the problem.
It is also the case that this same equation is an accurate model for the prior component of declarative memory, as was shown by \citeauthor{Anderson1991} in the original derivation, 
and as is supported in the results from this study.

>>>>

\textcite{Anderson1991} also used tasks similar to tag use on StackOverflow and Twitter when deriving the prior component of the declarative memory theory.
\citeauthor{Anderson1991} examined, for example, the frequency of word choice over time used for the title of articles for the New York Times,
and used the results to derive the power law equation for the prior term in the declarative memory model.
ACT-R's declarative memory theory claims that the system has evolved to make predictions that closely match the statistical structure of the environment.
Using a power-law equation to model future tag use based on past tag use is a reasonable statistical approach to the problem.
It is also the case that this same equation is an accurate model for the prior component of declarative memory, as was shown by \citeauthor{Anderson1991} in the original derivation, 
and as is supported in the results from this study.
